GSE158422: DNA methylation in Lung squamous cell carcinoma - gene methylation enrichment analysis

### 2023-10-02 figs/GSE158422_split.Rmd
working nicely

CORES=12

@@

lares <- lapply( seq(100,300,100) ,splitanalyze_la)

@@

alres <- lapply( seq(100,300,100) ,splitanalyze_al)

@@

aares <- lapply( seq(100,300,100) ,splitanalyze_aa)

@@

>>>>

CORES=28

@@

lares <- lapply( seq(100,5000,100) ,splitanalyze_la)

@@

alres <- lapply( seq(100,5000,100) ,splitanalyze_al)

@@

aares <- lapply( seq(100,5000,100) ,splitanalyze_aa)

@@

res <- do.call(rbind,lapply(list(laout,alout,aaout),colMeans))

rownames(res) <- c("la","al","aa")

res <- as.data.frame(res)
res %>%
  kbl(caption="overall summary") %>%
  kable_paper("hover", full_width = F)

Plot some data.

```{r,plots1,fig.height=5,fig.width=9}

par(mfrow=c(1,3))
barplot(res$p_comm,main="proportion common",names.arg=c("la","al","aa"))
barplot(res$p_uncom,main="proportion uncommon",names.arg=c("la","al","aa"))
barplot(res$p_disc,main="proportion discordant",names.arg=c("la","al","aa"))
